\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-28 notes/2loopNLSM.tex
Rearranged to prepare \bar{F}F discussion

Now we are prepared to discuss the one-loop case.

@@

Different kinds of CK.  We want global.  Global is the simplest
option, it is also the option that you would automatically get if you
had a color-dual Lagrangian.  By ``global'' we mean that
color-kinematics duality is satisfied in any kinematic configuration
of the integrand.  This is a much more stringent condition than
absolutely necessary.  There is reason to believe \cite{Bern:2015ooa}
\ace{Is this the cite you wanted?}  that global numerators cannot
always be found.  One resolution to the issue is to only demand
color-kinematics duality on the unitarity cuts of the integrand, i.e.,
in specific kinematic limits.  Enforcing Jacobi on the cuts is enough
to ensure that the squared integrand will correctly cut to gravity (or
whatever the squared theory might be).  When a globally color-dual
numerator cannot be found, another alternative explored in the
literature is to increase the size of the numerator ansatz by
enlarging the numerator from a polynomial to a rational function with
spurious singularities (cite Donal et al).  When global
color-kinematics fails, the hope is that it can be restored by
enlarging the size of the ansatz, either by giving the numerator of
each graph its own ansatz (first option described) or by promoting the
numerator to a non-local function (second option described).  Note
that a theory whose Lagrangian has color-kinematics duality would
naturally produce a globally color-dual integrand so the quest for a
global numerator is closely related to the existence of a Lagrangian
exhibiting color-kinematics duality.  Section X is devoted to
color-dual representations of the 4pt 2-loop NLSM integrand and the
analogous integrand for YM is treated in section Y.  Two-loop
color-dual integrands for pure YM have been investigated before but
only for a limited ansatz that manifests locality (cite Zvi et al
paper).  All of the N=4 SYM constructions below 5-loop are local.
Mention generalized double copy.

@@

Before proceeding, we note a strange property of the $n$-gon numerator for the pions. In this form, Jacobi relations produce \textit{non-vanishing} values for bubbles on external legs (BELs). However, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble. The BEL diagram can be reconstructed from the $n$-gon as follows:
\be
N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
\ee
where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
\be
N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
\ee
Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
\be
\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
\ee
where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$. Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram. 
\bibliographystyle{JHEP}
\bibliography{Refs_2loopNLSM}
\end{document}

>>>>

BCJ loves $\mathcal{L} = \bar{F} F$.
How this connects to SDYM, NLSM.
You can do tree and 1-loop.
Why the bowtie is so important.

@@

Different kinds of CK.  We want global.  Global is the simplest
option, it is also the option that you would automatically get if you
had a color-dual Lagrangian.  By ``global'' we mean that
color-kinematics duality is satisfied in any kinematic configuration
of the integrand.  This is a much more stringent condition than
absolutely necessary.  There is reason to believe \cite{Bern:2015ooa} that global numerators cannot
always be found.  One resolution to the issue is to only demand
color-kinematics duality on the unitarity cuts of the integrand, i.e.,
in specific kinematic limits.  Enforcing Jacobi on the cuts is enough
to ensure that the squared integrand will correctly cut to gravity (or
whatever the squared theory might be).  When a globally color-dual
numerator cannot be found, another alternative explored in the
literature is to increase the size of the numerator ansatz by
enlarging the numerator from a polynomial to a rational function with
spurious singularities (cite Donal et al).  When global
color-kinematics fails, the hope is that it can be restored by
enlarging the size of the ansatz, either by giving the numerator of
each graph its own ansatz (first option described) or by promoting the
numerator to a non-local function (second option described).  Note
that a theory whose Lagrangian has color-kinematics duality would
naturally produce a globally color-dual integrand so the quest for a
global numerator is closely related to the existence of a Lagrangian
exhibiting color-kinematics duality.  Section X is devoted to
color-dual representations of the 4pt 2-loop NLSM integrand and the
analogous integrand for YM is treated in section Y.  Two-loop
color-dual integrands for pure YM have been investigated before but
only for a limited ansatz that manifests locality (cite Zvi et al
paper).  All of the N=4 SYM constructions below 5-loop are local.
Mention generalized double copy.

@@

Before proceeding, we note a strange property of the $n$-gon numerator for the pions. In this form, Jacobi relations produce \textit{non-vanishing} values for bubbles on external legs (BELs). However, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble. The BEL diagram can be reconstructed from the $n$-gon as follows:
\be
N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
\ee
where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
\be
N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
\ee
Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
\be
\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
\ee
where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$. Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.

\section{Review of known theories}

\bibliographystyle{JHEP}
\bibliography{Refs_2loopNLSM}
\end{document}
